A framework for adaptive width control of dense contour-parallel toolpaths in {fused deposition modeling}\censornotice

### 2020-01-25 0_reviewer_response.tex

Fix double header of References.
\commits{7597b176f6a88ae98c8c7a4c791475af356b3da6}

Added patent notice and url to open source implementation.
\commits{
ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a
}
\paper{Intro}{
\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
}

Remove reference to the concept of `periphery' seeing as it was not really used.
\commits{
74227189eba03d13e18249f3235680691c6ebea9 % dont introduce
10bc58dc50f314e2d86f28ae6d8532fee3d20893 % don't use
a5c0d134c106876ae0edcb201eb270b66c11462f % typo near these^ commits
}
\paper{3.3 Center classification}{
\revise{The remainder is called peripheral.}{}
}
\paper{3.5 Beading}{
Now that we have determined the bead counts in the \revise{}{marked }central regions we will describe how the \revise{peripheral}{unmarked} regions are handled.
}

Lil
\commits{5f5c4c640d94010816e6d6d5934a2dc016b4d172
1662d3c4c3aa977bddd730ac59f1bc874b9eb574 % -''See ``
b108d7de4f1e1e9676d45cf24eea263af6b8b9c7 % width => widths
9d9f02edc43689c0970a74118e44a196cc11c729 % typos
87bed1e663ea831d8f52b0ccf4ef5eebaab32ade % typo
2e21687731d95a9a1315206531f0474fb924c6eb % spell check
}

### 2020-01-25 0_main.tex
undo censoring in master
remove \revise macro everywhere

	\censortrue
	\colorrevisefalse

@@

\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice}

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
\end{abstract}

@@

%\section*{References}
\interlinepenalty=100000 % prevents pdfendlink ended up accross pages error. see https://tex.stackexchange.com/a/449633/129190
\bibliography{99_mybib}

>>>>

	\censorfalse
	\colorrevisetrue

@@

\title{A framework for adaptive width control of dense contour-parallel toolpaths in {fused deposition modeling}\censornotice}

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply.

{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially {detrimental to the mechanical performance of} thin parts such as casings and microstructures.
Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which {reduces} extreme bead width deviation, {while limiting} the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 {layer outlines}.
We {statistically }validate the effectiveness of our framework and this novel scheme on a data set of {representative 3D models, }%sgd
{and physically validate it by developing a technique, called \emph{back pressure compensation}, for off-the-shelf FDM systems to effectively realize adaptive width.}
\end{abstract}

@@

\section*{References}
\interlinepenalty=100000 % prevents pdfendlink ended up accross pages error. see https://tex.stackexchange.com/a/449633/129190
\bibliography{99_mybib}

### 2020-01-25 10_applications.tex
remove \revise macro everywhere

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\censorbox{
\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\censorbox{
\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
}
\caption{\censor{TUD}}\label{applications_tud}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\censorbox{
\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
}
\caption{\censor{UM}}\label{applications_um}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\begin{subfigure}[t]{.3\figwidth}
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme \revise{}{($N=3$) }applied to various example application objects.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a tilted homogeneous gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\censorbox{
\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\censorbox{
\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
}
\caption{\censor{TUD}}\label{applications_tud}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\censorbox{
\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
}
\caption{\censor{UM}}\label{applications_um}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\begin{subfigure}[t]{.3\figwidth}
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme {($N=3$) }applied to various example application objects.
From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a tilted homogeneous gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}

### 2020-01-25 12_conclusions_future_work.tex
remove \revise macro everywhere

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{
we introduced beading schemes which improve on the state-of-the-art
and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
}

@@

\revise{We presented the}{The} inward distributed beading scheme
\revise{It}{} reduces the amount of beads with a width deviating extremely from the preferred bead width \revise{}{by changing the width of several beads near the center instead of only the center-most bead}.
\revise{, and thus it is}{It is therefore} expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
which in turn is helpful to efficiently simulate an FDM manufactured part.
\revise{
Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy of the shape of the outline contour is affected less by inaccuracies in the mechanical control system which realizes adaptive bead width.
}{}

The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
\revise{}{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}

\subsection{Future work}
The work presented here is evaluated mostly on a computational level, because the effectiveness of a mechanical system to accurately print an adaptive bead width interferes with the physical validation of our techniques.
Future research could be devoted to optimizing the distribution scheme to a specific hardware setup.
An accurate model of manufacturability, \revise{}{which relates }print speed\revise{, }{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
\revise{}{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
% If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.

>>>>

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas{,
we introduced beading schemes which improve on the state of the art
and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.
}

@@

{Compared to the state of the art,} the inward distributed beading scheme
reduces the amount of beads with a width deviating extremely from the preferred bead width {by changing the width of several beads near the center instead of only the center-most bead}.
{It is therefore} expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
which in turn is helpful to efficiently simulate an FDM manufactured part.

The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}

\medskip
{The presented framework is open source available at \\ \url{github.com/Ultimaker/libArachne}}

\subsection{Future work}
The work presented here is evaluated mostly on a computational level, because the effectiveness of a mechanical system to accurately print an adaptive bead width interferes with the physical validation of our techniques.
Future research could be devoted to optimizing the distribution scheme to a specific hardware setup.
An accurate model of manufacturability, {which relates }print speed, {layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
% If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.

### 2020-01-25 1_intro.tex
remove \revise macro everywhere

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
\revise{
Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
}{
Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
}

@@

One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
\citeauthor{Ding2016a} developed a toolpath strategy for wire and arc additive manufacturing which produces a width variation typically lower than a factor of $3$, but is \revise{sometimes}{} far greater\revise{}{ for some parts}~\cite{Ding2016a,Xiong2019}.
However, the range of widths manufacturable by FDM systems is limited.
A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
%Therefore, a limited range of widths is required by the hardware system.

The current \revise{state-of-the-art}{state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
% (0.8 + 1) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a homogeneity assumption.
\revise{
Therefore, a narrower range of widths is desirable.
}
{We therefore reduce the bead width range by distributing the workload from the centermost bead over neighboring beads.}

In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
\revise{
For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
}{Furthermore we present an approach to accurately realize adaptive bead width.
}
See \cref{intro_wedge_distributed}. 
% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
% Some such toolpath generation techniques have already been developed.

\begin{figure}\centering
\setlength{\figwidth}{.9\columnwidth}
\setlength{\figwidthTwo}{.05\columnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicated in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
}
\label{intro_wedge}
\end{figure}

Our contributions are as follows:
\begin{itemize}
\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme for FDM printing which
\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
\revise{}{
\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
}
\end{itemize}

\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}

>>>>

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
{
Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
}

@@

One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
\citeauthor{Ding2016a} developed a toolpath strategy for wire and arc additive manufacturing which produces a width variation typically lower than a factor of $3$, but is  far greater{ for some parts}~\cite{Ding2016a,Xiong2019}.
However, the range of widths manufacturable by FDM systems is limited.
A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
%Therefore, a limited range of widths is required by the hardware system.

The current {state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads {within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
% (0.8 + 1) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
See \cref{intro_wedge_centered}.
Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g. linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a homogeneity assumption.

{We therefore reduce the bead width range by distributing the workload from the centermost bead over neighboring beads.}

In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
{Furthermore we present an approach to accurately realize adaptive bead width.
}
See \cref{intro_wedge_distributed}. 
% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
% Some such toolpath generation techniques have already been developed.

\begin{figure}\centering
\setlength{\figwidth}{.9\columnwidth}
\setlength{\figwidthTwo}{.05\columnwidth}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
\end{subfigure}
\caption{
Illustration of different toolpath{s} for a shape {showcasing a range of shape radii }{(black)}.
{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are {indicated} in red and blue, respectively.
\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with {less extreme widths}.
}
\label{intro_wedge}
\end{figure}

Our contributions are as follows:
\begin{itemize}
\item A geometric framework {allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
\item A specific beading scheme  which
{furthermore} reduces the amount of {variation} in the extrusion widths compared to {the state of the art to be below a factor of 2.}

{
\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
}
\end{itemize}

### 2020-01-25 2_related_work.tex
lil typo
remove \revise macro everywhere

% criteria for toolpath generation
The toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object~\cite{N.Turner2014,ahn2002anisotropic}.
FDM calls for toolpaths with several desirable properties.
First, the extrusion path should be as continuous as possible.
A discontinuous path requires to stop and restart material extrusion.
For certain materials such as TPU, this could lead to printing defects or even print failure~\cite{KUIPERS2019CAD}.
Second, the toolpath is preferred to be smooth.
Sharp turns require to reduce the movement speed of the nozzle, and so this prolongs the printing process.
Third, the extruded path should cover a the region of the contour without gaps.
Such underfill negatively influences the mechanical performance of the parts.
Fourth, the extrusion paths should not overlap with one another.
Such overfill causes a pressure build up in the mechanical system, which leads to overextrusion in further paths and in extreme cases cause print failure~\cite{KUIPERS2019CAD}.
An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
Our method is primarily concerned with minimizing under- and overfill within horizontal cross-sections.

@@

% the idea, and (some of) the most related work
Reducing under- and over-filling can be accurately achieved by making use over adaptive depisition width.
Adaptive width can be used to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
%Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
\citeauthor{kao1998optimal} propose smooth adaptive toolpaths based on the medial axis skeleton of the boundary contour~\cite{kao1998optimal}.
Their approach handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
However, this extension inherits a problem in the original method:
from any point in the skeleton to the boundary, the number of toolpaths is constant.
Since the distance may vary considerably for shapes with both large and small features, this strategy leads to a toolpath with widths that may differ by a factor beyond $3$, which is impossible for some FDM systems.
\citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting variation of width in the center is still up to a factor of $2$ (see \cref{intro_wedge_centered}).
In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme deviations in width (see \cref{intro_wedge_distributed}).

>>>>

% criteria for toolpath generation
The toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object~\cite{N.Turner2014,ahn2002anisotropic}.
FDM calls for toolpaths with several desirable properties.
First, the extrusion path should be as continuous as possible.
A discontinuous path requires to stop and restart material extrusion.
For certain materials such as TPU, this could lead to printing defects or even print failure~\cite{KUIPERS2019CAD}.
Second, the toolpath is preferred to be smooth.
Sharp turns require to reduce the movement speed of the nozzle, and so this prolongs the printing process.
Third, the extruded path should cover the region of the contour without gaps.
Such underfill negatively influences the mechanical performance of the parts.
Fourth, the extrusion paths should not overlap with one another.
Such overfill causes a pressure build up in the mechanical system, which leads to overextrusion in further paths and in extreme cases cause print failure~\cite{KUIPERS2019CAD}.
An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
Our method is primarily concerned with minimizing under- and overfill within horizontal cross-sections.

@@

% the idea, and (some of) the most related work
Reducing under- and over-filling can be accurately achieved by making use over adaptive {deposition} width.
Adaptive width can be used to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
%Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
\citeauthor{kao1998optimal} propose smooth adaptive toolpaths based on the medial axis skeleton of the boundary contour~\cite{kao1998optimal}.
Their approach handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
However, this extension inherits a problem in the original method:
from any point in the skeleton to the boundary, the number of toolpaths is constant.
Since the distance may vary considerably for shapes with both large and small features, this strategy leads to a toolpath with widths that may differ by a factor beyond $3$, which is impossible for some FDM systems.
\citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting variation of width in the center is still up to a factor of {$3.6$} (see \cref{intro_wedge_centered}).
In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme {variation} in width (see \cref{intro_wedge_distributed}).
